Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
Cleaned up table

\begin{table}
       \centering
       \begin{tabular}[Ht]{|c"c|c|c|c|}
       \hline
       Mode &  \multicolumn{2}{c}{Main} & \multicolumn{2}{c}{Sub} \\

       \hline
       \textbf{Change} & \textbf{Prediction} & \textbf{Actual} & \textbf{Prediction} & \textbf{Actual} \\
       \hline    
       Example Code & U &      R\textsubscript{ef} &   R\textsubscript{ef} &   U \\
       \hline
       Documentation & U &      U &      Ref &   Ref \\
       \hline
       Interfaces & G &    P &    P &    G \\
       \hline
       Error Handling & P &    P &    G &    G \\
       \hline
       3rd Party & A &      A &      N/A &           N/A \\
       \hline
       axaudio & E &     E &     N/A &           N/A \\
       \hline
       axptz & E &     E &     N/A &           N/A \\
       \hline
       axstorage & E &     E &     N/A &           N/A \\
       \hline
       axserialport & E &     E &     N/A &           N/A \\
       \hline
       axevent & E &     E &     G &    G \\
       \hline
       axhttp & E &     E &     G &    G \\
       \hline
       ax\_parameter & E &     E &     G &    G \\
       \hline
       Burst Mode & R\textsubscript{ed} &     R\textsubscript{ed} &     N/A &           N/A \\
       \hline

>>>>

\begin{table}
       \centering
       \begin{tabular}[Ht]{|c"c|c|c|c|}
       \hline

       Mode                        & \multicolumn{2}{c}{Main}                              & \multicolumn{2}{c}{Sub}                 \\ \hline

       \textbf{Change}      & \textbf{Prediction}       & \textbf{Actual}           & \textbf{Prediction}       & \textbf{Actual}    \\ \hline    
       Example Code         & U                         & R\textsubscript{ef}       & R\textsubscript{ef}       & U                  \\ \hline
       Documentation        & U                         & U                         & Ref                       & Ref                \\ \hline
       Interfaces           & G                         & P                         & P                         & G                  \\ \hline
       Error Handling       & P                         & P                         & G                         & G                  \\ \hline
       3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
       axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
       axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
       axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
       axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
       axevent              & E                         & E                         & G                         & G                  \\ \hline
       axhttp               & E                         & E                         & G                         & G                  \\ \hline
       ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
       Burst Mode           & R\textsubscript{ed}       & R\textsubscript{ed} &     N/A                         & N/A                \\ \hline
